Price of Anarchy for Mean Field Games

### 2018-07-25 PoA.tex
removed t* in prop 4

	Now we are ready to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,t^*]$ and $[t^*,T]$.	
	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$. We have:
	\begin{equation}
	\begin{split}
		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} &\leq \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{t^*} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{t^*}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\ 
		&=  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1^{b_2} + I_2^{b_2} \right),
	\end{split}
	\label{eq:I_1_plus_I_2}
	\end{equation}
	where:
	\begin{IEEEeqnarray*}{rCl}
	I_1^{b_2} &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{t^*} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
	\right) dt \\
	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{t^*} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt, 
	\end{IEEEeqnarray*}
	and:
	$$
		I_2^{b_2} = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{t^*}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
	$$

	Fix $\epsilon>0$. In the following, we show that $I_1^{b_2} \leq \epsilon$ and $I_2^{b_2} \leq \epsilon$ for large $b_2$.
	% the term I_1
	First, consider $I_1^{b_2}$. Recall that for $t \in[0,T/2]$, we have $\lim_{b_2 \to \infty}h_u(b_2,t) = c_u$ and $\lim_{b_2 \to \infty}h_w(b_2,t) = c_w$, and for all $b_2 \geq b_2^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing, and thus, $[0,T/2] \ni s \mapsto h_u(b_2,t)$ and $[0,T/2] \ni s \mapsto h_w(b_2,t)$ are increasing. (Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let $\zeta_2 =\min \{\frac{1}{2}\sqrt{\epsilon c}e^{-T(b_1+\bar{b}_2)},\frac{c}{2}\}$. Then there exists $b_2^{*,I_1}  > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
	\begin{equation*}
	\begin{array}{lclclclcl}
		c - \zeta_2 &\leq& h_u(b_2,0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2 ) &\leq& c + \zeta_2, \\
		c - \zeta_2 &\leq& h_w(b_2,0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2 ) &\leq& c + \zeta_2.
	\end{array}
	\end{equation*}
	Thus, if $t^* < \frac{T}{2}$, then for any $t \in [0,t^*]$ and $b_2 \geq b_2^{*,I_1}$, we have:
	$$
		\vert h_u(b_2, t) - h_w(b_2,t) \vert^2 \leq  4 \zeta_2^2 \quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c - \zeta_2) t \geq \frac{c}{2}\cdot t.
	$$
	Therefore,
	\begin{IEEEeqnarray}{rCl}
		I_1^{b_2} &\leq& 4\zeta_2^2e^{2T(b_1 + \bar{b}_1)} \cdot\frac{(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{t^*} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot \frac{c}{2}\cdot t \right) dt \nonumber \\
		&=& 2\zeta_2^2 \cdot \frac{e^{2T(b_1 + \bar{b}_1)}}{\frac{c}{2}} \left( 1 - e^{ - \frac{2(b_2 + \bar{b}_2) \frac{c}{2}}{r + \bar{r}(1-\bar{s})^2}  t^* } \right) \\
		&\leq& \frac{4e^{2T(b_1 + \bar{b}_1)}}{c}\cdot \zeta_2^2\\
		&\leq&\epsilon, 
	\label{eq:I1_ineq_b2_infinity}
	\end{IEEEeqnarray}
	where the last inequality comes from the definition of $\zeta_2$.

	% check I_2
	Next, consider $I_2^{b_2}$ with $t^*$ as in equation (\ref{eq:t^*_b2_infty}). 
	Since the functions $s \mapsto u_s^{\bar{b}_2}$, $s \mapsto w_s^{\bar{b}_2}$ and $s \mapsto \bar{x}_s^{MFG,\bar{b}_2}$ are continuous over $[t^*,T]$, then the functions $\displaystyle t \mapsto \int_{t^*}^T u^{\bar{b}_2}_s ds$ and $\displaystyle t \mapsto \int_{t^*}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[t^*,T]$ and differentiable over $(t^*,T)$. We can apply the mean value theorem and deduce that for a fixed $b_2$, there exists a time point $t_1^{b_2}$ with $t^* < t_1^{b_2} < T$ such that:
	\begin{equation}
		I_2^{b_2} = (T-t^*) \cdot \frac{\left(u_{t_1^{b_2}}^{b_2} - w_{t_1^{b_2}}^{b_2}\right)^2 e^{2(b_1 + \bar{b}_1)t_1^{b_2}} }{r + \bar{r}(1-\bar{s})^2}  \cdot  (b_2 + \bar{b}_2)^3 e^{ -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t_1^{b_2}} h_u(b_2,s) ds }.
	\label{eq:I2_b2_infity_Mean_Value}
	\end{equation}	
	We know from equations (\ref{eq:u_t_bound}) and (\ref{eq:w_t_bound}) that for all $b_2 \geq b_2^{*,upper}>b_2^{*,lower}$ and all $t \in [0,T]$:
	\begin{equation*}
		\vert u_t^{b_2} - w_t^{b_2} \vert \leq \sup_{0 \leq t \leq T} \vert u_t^{b_2} \vert + \vert w_t^{b_2} \vert  \leq 2M,
	\end{equation*}
	and 
	\begin{equation*}
		\int_0^{t_1^{b_2}} h_u(b_2,s) ds \geq \int_0^{t^*} h_u(b_2,s) ds \geq t^* m_u.
	\end{equation*}
	Combining this with (\ref{eq:I2_b2_infity_Mean_Value}) gives:
	\begin{equation*}
		I_2^{b_2} \leq  \frac{4 T M^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^3 e^{- \frac{2 t^*  m_u}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2) } = \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \xrightarrow[b_2 \to \infty]{} 0,
	\end{equation*}
	where $\kappa_3 = \frac{4 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{2 t^*  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$. 	
	Hence, there exists $b_2^{*,I_2} > b_2^{*,upper}>b_2^{*,lower}$ such that for all $b_2 \geq b_2^{*,I_2}$: 
	\begin{equation}
		I_2^{b_2} \leq \epsilon.
	\label{eq:I2_b2_infty}
	\end{equation}

>>>>

	Now we are ready to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,\frac{T}{2}]$ and $[\frac{T}{2},T]$.	
	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$. We have:
	\begin{equation}
	\begin{split}
		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} &\leq \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{\frac{T}{2}}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\ 
		&=  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1^{b_2} + I_2^{b_2} \right),
	\end{split}
	\label{eq:I_1_plus_I_2}
	\end{equation}
	where:
	\begin{IEEEeqnarray*}{rCl}
	I_1^{b_2} &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
	\right) dt \\
	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt, 
	\end{IEEEeqnarray*}
	and:
	$$
		I_2^{b_2} = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{\frac{T}{2}}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
	$$

	Fix $\epsilon>0$. In the following, we show that $I_1^{b_2} \leq \epsilon$ and $I_2^{b_2} \leq \epsilon$ for large $b_2$.
	% the term I_1
	First, consider $I_1^{b_2}$. Recall that for $t \in[0,T/2]$, we have $\lim_{b_2 \to \infty}h_u(b_2,t) = c_u$ and $\lim_{b_2 \to \infty}h_w(b_2,t) = c_w$, and for all $b_2 \geq b_2^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing, and thus, $[0,T/2] \ni s \mapsto h_u(b_2,t)$ and $[0,T/2] \ni s \mapsto h_w(b_2,t)$ are increasing. (Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let $\zeta_2 =\min \{\frac{1}{2}\sqrt{\epsilon c}e^{-T(b_1+\bar{b}_2)},\frac{c}{2}\}$. Then there exists $b_2^{*,I_1}  > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
	\begin{equation*}
	\begin{array}{lclclclcl}
		c - \zeta_2 &\leq& h_u(b_2,0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2 ) &\leq& c + \zeta_2, \\
		c - \zeta_2 &\leq& h_w(b_2,0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2 ) &\leq& c + \zeta_2.
	\end{array}
	\end{equation*}
	Thus, for any $t \in [0,\frac{T}{2}]$ and $b_2 \geq b_2^{*,I_1}$, we have:
	$$
		\vert h_u(b_2, t) - h_w(b_2,t) \vert^2 \leq  4 \zeta_2^2 \quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c - \zeta_2) t \geq \frac{c}{2}\cdot t.
	$$
	Therefore,
	\begin{IEEEeqnarray}{rCl}
		I_1^{b_2} &\leq& 4\zeta_2^2e^{2T(b_1 + \bar{b}_1)} \cdot\frac{(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot \frac{c}{2}\cdot t \right) dt \nonumber \\
		&=& 2\zeta_2^2 \cdot \frac{e^{2T(b_1 + \bar{b}_1)}}{\frac{c}{2}} \left( 1 - e^{ - \frac{2(b_2 + \bar{b}_2) \frac{c}{2}}{r + \bar{r}(1-\bar{s})^2}  \frac{T}{2} } \right) \\
		&\leq& \frac{4e^{2T(b_1 + \bar{b}_1)}}{c}\cdot \zeta_2^2\\
		&\leq&\epsilon, 
	\label{eq:I1_ineq_b2_infinity}
	\end{IEEEeqnarray}
	where the last inequality comes from the definition of $\zeta_2$.

	% check I_2
	Next, consider $I_2^{b_2}$. 
	Since the functions $s \mapsto u_s^{\bar{b}_2}$, $s \mapsto w_s^{\bar{b}_2}$ and $s \mapsto \bar{x}_s^{MFG,\bar{b}_2}$ are continuous over $[\frac{T}{2},T]$, then the functions $\displaystyle t \mapsto \int_{\frac{T}{2}}^T u^{\bar{b}_2}_s ds$ and $\displaystyle t \mapsto \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[\frac{T}{2},T]$ and differentiable over $(\frac{T}{2},T)$. We can apply the mean value theorem and deduce that for a fixed $b_2$, there exists a time point $t_1^{b_2}$ with $\frac{T}{2} < t_1^{b_2} < T$ such that:
	\begin{equation}
		I_2^{b_2} = (T-\frac{T}{2}) \cdot \frac{\left(u_{t_1^{b_2}}^{b_2} - w_{t_1^{b_2}}^{b_2}\right)^2 e^{2(b_1 + \bar{b}_1)t_1^{b_2}} }{r + \bar{r}(1-\bar{s})^2}  \cdot  (b_2 + \bar{b}_2)^3 e^{ -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t_1^{b_2}} h_u(b_2,s) ds }.
	\label{eq:I2_b2_infity_Mean_Value}
	\end{equation}	
	We know from equations (\ref{eq:u_t_bound}) and (\ref{eq:w_t_bound}) that for all $b_2 \geq b_2^{*,upper}>b_2^{*,lower}$ and all $t \in [0,T]$:
	\begin{equation*}
		\vert u_t^{b_2} - w_t^{b_2} \vert \leq \sup_{0 \leq t \leq T} \vert u_t^{b_2} \vert + \vert w_t^{b_2} \vert  \leq 2M,
	\end{equation*}
	and 
	\begin{equation*}
		\int_0^{t_1^{b_2}} h_u(b_2,s) ds \geq \int_0^{\frac{T}{2}} h_u(b_2,s) ds \geq \frac{T}{2} m_u.
	\end{equation*}
	Combining this with (\ref{eq:I2_b2_infity_Mean_Value}) gives:
	\begin{equation*}
		I_2^{b_2} \leq  \frac{4 T M^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^3 e^{- \frac{2 \frac{T}{2}  m_u}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2) } = \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \xrightarrow[b_2 \to \infty]{} 0,
	\end{equation*}
	where $\kappa_3 = \frac{4 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{2 \frac{T}{2}  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$. 	
	Hence, there exists $b_2^{*,I_2} > b_2^{*,upper}>b_2^{*,lower}$ such that for all $b_2 \geq b_2^{*,I_2}$: 
	\begin{equation}
		I_2^{b_2} \leq \epsilon.
	\label{eq:I2_b2_infty}
	\end{equation}
